%Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}

%Please include a clear, concise, and descriptive title
\title{An Essay on Game Platform Constraints and their Historial Context}

%Please do not change the subtitle
\subtitle{COMP130 - Game Platform History Essay}

%Please put your student number in the author field
\author{DO NOT WRITE YOUR NAME\\Put Your Student Number (On Your ID Card) Here}

\begin{document}

\maketitle

\abstract{Please include an abstract of at most 100 words (these do not count towards your word count). For example: This short essay introduces the PDP-1 computer as a game platform and discusses how it contributed to the development of `hacker' culture in the early 1970s. It argues that despite the highly constained technologies used at the Hingham Instute at MIT, engaging game design is possible. The development of the game \textit{SpaceWar!} explifies this, inspiring a movement to creatively repurpose computers for entertainment purposes.}

\section{Introduction}

Write your introduction here. A brief introduction is recommended, which should outline key details of the platform, motivate the work, and provide a roadmap of key points to the reader. The motivation is quite important here, as essays should have a contribution (i.e., what is the point of the essay, and what does the reader take away from the essay) and the link between the motivation (in the introduction) and the contribution (in the conclusion) should be made clear.

\section{Main Body -- Please Change This Heading}

Write the main body of your essay here. Remember, there should be descriptive components \textit{as well as} analytical and evaluative components. You must not simply rephrase and represent your sources, but demonstrate analysis and evaluation through your argument. Any claims that you make should be defended through evidence and/or appropriate reasoning. Use the reccommended reading (i.e., \cite{evans2006invisible, squid-news, atariage}) where appropriate. Be as concise as possible. Please see the assignment brief for additional guidence. 

Ensure that you use an appropriate structure for your main body. You may use multiple paragraphs and/or multiple section headings. Emphasise the flow of the essay and the direction of the argument. It is more important to argue fewer points well, than have more points argued poorly.

\section{Conclusion}

Write your conclusion here. The conclusion should do more than summarise the essay, making clear the contribution of the work and highlighting key points, limitations, and outstanding questions. It should not introduce any new content or information.

% Please use the ieeetran or acm style only
\bibliographystyle{ieeetran}
\bibliography{game-platform-history-references}

\end{document}